---
title: 'Challenge: Identify the Penguin'
author: "Team #X"
format: html
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: true
  error: false
---

Team Member Names: 



Run this code chunk.

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(ggformula)
library(mosaic)
```


## Read in the full data

Run the code chunk to read in the data.

```{r}
#| label: load-data
penguins <- read_csv("penguins.csv", show_col_types = FALSE)
```


If you want to add the bill ratio variable, run the following code:

```{r}
#| label: add-bill-ratio
penguins <- mutate(penguins, bill_ratio = bill_length_mm/bill_depth_mm)
```



## Measurements of your Penguin

There are some penguins that were measured, but the species wasn't recorded. (Yikes!) Import the data containing these penguin measurements. 

```{r}
#| label: read-sample
penguin_samples <- read_csv("peng_samp.csv", show_col_types = FALSE)
```

Run the following code, replacing the provided number with your group number (currently it is set to Group #1). This is the measurements from your team's assigned unidentified penguin.

```{r}
#| label: get-your-penguin
filter(penguin_samples, Group == 1)
```

(this data set is only used to give you your penguin's measurements)




## Identification of your Penguin

Your task is to determine which species your penguin likely is by using the `penguins` dataset. You may use any graphic, summary statistic, or variable to help determine your species. You just need to be sure to back up your identification with evidence. 

```{r}
# add additional code chunks to calculate the summary statistics or create any graphics needed to identify your penguin. 
```
 



What is your identification of your penguin? Justify your classification using statistical evidence. Be prepared to share your answer & justification with the class.

> Insert your answer here


